### 2022-01-17 src-latex/figs/eval-ocr-ner.tex
Update eval with precision/recall/fscore

  \matrix[taggedalignment] (E2) [below=of E1.west, anchor=west]
  {
    Alubert& (Prosper),⎵ &horlogerie&,⎵  &r, de la Ius-⎵sienne&,&78&⎵⎵\\
  };

@@

  \draw[-latex] (C.south) -- ++(0,-1) node[midway,right,font=\small] {OCR Q.A.} node[below] {CER = 24\%};
  \draw[-latex] (D.south) -- ++(0,-1) node[midway,right,font=\small] {NER gt.};
  \draw[-latex] (C.south east) |- (E2) node[pos=0.75,below, font=\it] {NER Prediction};
  \draw[-latex] (E2.south) -- ++(0,-1) node[midway,right,font=\small] {NER Q.A.} node[below] {FIXME\%};
\end{tikzpicture}

>>>>

  \matrix[taggedalignment] (E2) [below=of E1.west, anchor=west]
  {
    & Alubert (Prosper),⎵ &horlogerie&,⎵  &r, de la Ius-⎵sienne&,&78&⎵⎵\\
  };

@@

  \draw[-latex] (C.south) -- ++(0,-1) node[midway,right,font=\small] {OCR Q.A.} node[below] {CER = 24\%};
  \draw[-latex] (D.south) -- ++(0,-1) node[midway,right,font=\small] {NER reference.};
  \draw[-latex] (C.south east) |- (E2) node[pos=0.75,below, font=\it] {NER Prediction};
  \draw[-latex] (E2.south) -- ++(0,-1) node[midway,right,font=\small] {NER Q.A.}
  node[below] {Precision = 33\%, Recall = 25\%, F-score = 0.4};
\end{tikzpicture}

### 2022-01-17 src-latex/parts/50-xp-setup.tex
Update eval with precision/recall/fscore

Next, a NER system extracts the named entities from the text of each entry outputed by the OCR and the \textbf{NER Q.A.}
is performed. The NER system outputs a text with tags that enclose the entities. To assess the quality of the entity
extraction, we rely on the same technique as for the OCR evaluation. The predicted text is aligned with the reference
text and the tags are projected in the alignment. Then, the CER \nathalie{non ici ce sont la précision, le rappel et la F-mesure qui sont calculées} is computed between each entity of the alignment and the
groundtruth as illustrated on \cref{fig.eval-ocr-ner}.

>>>>

Next, a NER system extracts the named entities from the text of each entry output by the OCR and the \textbf{NER Q.A.}
is performed. The NER system outputs a text with tags that enclose the entities. To assess the quality of the entity
extraction, we rely on a technique similar as for the OCR evaluation. The predicted text is aligned with the reference
text and the tags are projected in the alignment. Then, the precision, recall and F-measure are computed considering
only the exact matches between entities.

\begin{align}
    \mathrm{precision} &= \frac{\text{\#exact matches}}{\text{\#entries in prediction}} & \mathrm{recall} &= \frac{\text{\#exact matches}}{\text{\#entries in reference}}
\end{align}

The whole process is illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the GOLD text are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the GOLD tags to build the tagged NER reference string. Finally, the NER system runs on the
OCR text; its output is compared to the NER reference string. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matching in the reference (recall). It follows an overall f-score of 0.4.
